Collaborative Visual Analysis on the Web with RCloud

### 2015-06-26 interviews.tex
s/prefered/preferred/

\paragraph*{Web is limiting} Although most analysts appreciated RCloud's sharing features,
it was not a popular tool for exploratory data analysis.
All analysts with R experience prefered to do analysis in another
tool, then paste code into RCloud for sharing, because the web interface got in the
way of their work.

>>>>

\paragraph*{Web is limiting} Although most analysts appreciated RCloud's sharing features,
it was not a popular tool for exploratory data analysis.
All analysts with R experience prefeered to do analysis in another
tool, then paste code into RCloud for sharing, because the web interface got in the
way of their work.
